\documentclass[12pt,twoside,a4paper]{article}
\usepackage[utf8]{inputenc}

\usepackage[colorlinks=false]{hyperref}

%\usepackage[fleqn]{amsmath}
\usepackage{import}
\usepackage{amsmath, nccmath}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{multirow}
\usepackage{stmaryrd}
\usepackage{cleveref}
\usepackage{float}
\usepackage{booktabs}
\usepackage[nottoc,numbib,notlof,notlot]{tocbibind}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{setspace}
\usepackage{placeins}
\usepackage[margin=1cm,labelfont=bf]{caption}
\usepackage[margin=0.25cm,labelfont=bf]{subcaption}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{lscape}
\usepackage{diagbox}
\usepackage{comment}


\renewcommand\thesubfigure{\roman{subfigure}}

\usepackage{fancyhdr}
\setlength{\headheight}{15.34767pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\rightmark}
\fancyhead[RE,LO]{\leftmark}
\fancyfoot[C]{\thepage}

\fancypagestyle{contents}{% define a custom header OPTION 1 to be applied to specific pages
    \fancyhf{}
    \fancyhead[RE,LO]{\leftmark}
    \fancyfoot[C]{\thepage}
}


\numberwithin{equation}{section}

\usepackage{placeins}
\usepackage{graphicx}
\graphicspath{ {./Images/} }
\usepackage[margin=1.1in]{geometry}
\renewcommand{\arraystretch}{1.7}

\doublespacing

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\usepackage[toc,page]{appendix}

\usepackage[backend=biber, style=numeric-comp, sorting=none, uniquename=init, giveninits=true, natbib=true, doi=false,url=false,isbn=false]{biblatex}
\addbibresource{references.bib}
\setcounter{biburlnumpenalty}{100}
\setcounter{biburlucpenalty}{100}
\setcounter{biburllcpenalty}{100}

\DeclareSourcemap{
    \maps{
        % Replace '{\_}', '{_}' or '\_' with just '_' in doi field
        \map{
            \step[
                fieldsource=doi,
                match=\regexp{\{\\\_\}|\{\_\}|\\\_},
                replace=\regexp{\_}
            ]
        }
        % Replace '{\_}', '{_}' or '\_' with just '_' in url field
        \map{
            \step[
                fieldsource=url,
                match=\regexp{\{\\\_\}|\{\_\}|\\\_},
                replace=\regexp{\_}
            ]
        }
    }
}

\newbibmacro{string+doiurlisbn}[1]{%
  \iffieldundef{doi}{%
    \iffieldundef{url}{%
      #1%
    }{%
      \href{\thefield{url}}{#1}%
    }%
  }{%
    \href{http://dx.doi.org/\thefield{doi}}{#1}%
  }%
}

\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
\DeclareFieldFormat[article,incollection]{title}%
    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}


\allowdisplaybreaks

\begin{document}

\input{titlePage}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\rightmark}
\fancyhead[RE,LO]{\leftmark}
\fancyfoot[C]{\thepage}

\newpage
\section*{Abstract}
With the aim to form a fast mesh-free method for solving Stokes flow in biological fluid dynamics, we consider options to accelerate the method of regularised stokeslets. Although simple to implement, the method of regularised stokeslets comes with a large computational cost as traditional methods require the creation of large dense matrices which quickly become computationally challenging to work with. We consider the use of the Kernel Independent Fast Multipole method (KIFMM) to compute the interactions between regularised stokeslet points. In this case, we show that the KIFMM method can be used to quickly and efficiently evaluate the matrix-vector product when compared to the direct product method. We then consider cases which require the solving of linear systems involving the stokeslet matrix. For the case of augmented problems such as the force-free swimming problem, we derive an appropriate preconditioner to aid convergence when using the Generalized Minimal RESidual method (GMRES). Our main contribution is the adaptation of the KIFMM method to use nearest neighbour interpolation in order to reduce the overall number of degrees of freedom in our system and aid overall computation times. This method shows promise, dramatically reducing computation times for certain systems, however more work is needed to form an optimal method for problems. 

\newpage
\section*{Acknowledgements}
I would like to thank the following people for helping me through this project and allowing me to write something I am incredibly proud of. Thank you to my supervisor Professor Dave Smith whose expertise and insight guided me throughout the project. To my parents and Nick Wicks who have proofread so many drafts of this paper. And finally to the University of Birmingham's BlueBEAR HPC service for the generous amounts of computing power which allowed for the computations in this project to be possible. 


\begin{singlespace}
\pagestyle{contents}
\newpage
{
  \hypersetup{hidelinks}
  \tableofcontents
}

\newpage
\listoffigures
\newpage
\listoftables
\listofalgorithms
\end{singlespace}

\pagestyle{fancy}

\newpage
\input{Introduction}
\input{MethodofRegularizedStokeslets}
\input{Nbody}
\input{KIFMM}
\input{Nearest}
\input{Hybrid}
\input{NumericalSimulations}
\input{Discussion}
\newpage
\input{Appendix}

\FloatBarrier

\pagestyle{contents}
\begin{singlespace}
\printbibliography[heading=bibintoc]
\end{singlespace}
\end{document}
